%Her beskrives de eventuelle konflikter der er opstået gennem projektforløbet – hvor disse konflikter har haft indflydelse på udviklingsprocessen. Hvad var årsagen til de opstod, og hvad der gjort for at løse konflikterne?
\chapter{Conflict handling}
When we started working on this project, we created a requirements specification for the project that we thought was the one we were supposed to make. It was based on a meeting with EIVA and the problem description that we got in the pre-bachelor project. When we sent this requirements specification to EIVA, which we worked for at that point, we didn't receive any feedback for one week. After this, we ended up calling them and not getting a response the first time. When we finally got a hold of them, they explained that they were very busy at the moment, but that we could arrange a meeting at "EIVA days" at Aarhus harbour, where they would present products to their customers. We got there in the morning and waited till the afternoon before they had time to meet us. It turned out that there were some major misunderstandings on our part regarding what they meant by an autopilot system. This was very frustrating for us, and we discussed this at length with our supervisor. We ended up continuing with the project that we specified in the requirements specification, and ended the collaboration with EIVA. 

We also had one internal conflict in the middle of the project. This conflict was based on differing perspectives on work planning and management. We solved the conflict at a meeting where we ended up discussing it. The discussion ended up in a renewed expectations on how we were to work together.

% Eiva konflikt
% Efterårs ferie konflikt
