%Her kan beskrives hvordan projektet er administreret mht. til konfigurationsstyring (principper, værktøjer), anvendelse af logbog, intern kommunikation (mail, Facebook), etc. Hvis I har anvendt Scrum kan anvendelsen af taskboard, backlog, sprint retrospective, sprint review og burndown charts beskrives her.
\chapter{Project administration}
To administer project artefacts and source code, we have used a git repository. More specifically we have used GitHub\cite{github}, and their GitHub Desktop application\cite{github_desktop}. On GitHub we have three repositories; the first one is for the pre-bachelor project, the two other repositories are for the actual bachelor project. One is called Boat-autopilot and is used for the entire source code of the project. The other repository is called Boat-autopilot-documentation and as the name states holds all of the documentation and other project artefacts.

To keep track of what was done each day of the project, we started out writing logbooks. This worked very well when most of the work was done in collaboration. But when the work shifted to individual work, we slowly drifted from used logbooks, and instead moved over to Trello. Trello keeps track of what is done to all tasks and when it is done. So we found logbooks to be rather redundant at that point. 

For the entire project we have used Facebook messenger~\cite{facebook-messenger} to get in touch with each other, which is just an easy way to communicate, both on the computer or on the phone. 

 
% Konfigurationstyring
%% Git
%% Struktur
%% Emails
%
% Logbog
% Intern kommunikation, facebook messenger
