%Her beskrives hvordan I udførte arbejdsfordelingen i fm. produktets udvikling. Valgte I den sikre vej, hvor I hver kunne anvende jeres forhåndsviden – eller valgte I en udfordrende vej, hvor I hver bevidst tilstræbte at arbejde med ukendte områder? Hvis I har anvendt Scrum kan anvendelsen af Scrum taskboard beskrives her. I kan her beskrive kort hvordan arbejdsfordelingen fungerede.

\chapter{Work distribution}
For managing the project we used a scrum like task board. First off the task board was on a physical bulletin board, but later it was moved to the online tool Trello \cite{trello}. 

The task board was divided up into 5 sections; Backlog, doing, review, reviewed, and done. The backlog is the place where all the tasks for the project reside, that is every thing from implementation task, to documentation or research. The doing section is used to signify that a task is currently being worked on, this minimizes the risk of parallel work. When a task in doing is done it is move to the review section, where the other group member looks at what has been done and gives comments. After review the task is moved to the reviewed section, where the original owner of the task decides whether it goes back in the backlog for further work, or it goes to the done section.

Even though the task board is a scrum like board, we did not follow normal scrum. The entire project was more or less one sprint, that means that if one wants to work on a task in the backlog the person can just go a head. 

The distribution of task is rather simple, if you find a task interesting or feel like doing that task, then you just put it in doing and its yours. A lot of time tho before a task has prerequisite tasks, that need to be done before it can be completed. That way the less interesting task also gets done. In the beginning of the project we also used the task board, but a lot of the task were done together. 

This way of distributing the work task of the project means that, if one want to learn something new by working on a task in the unknown one can do it. But if schedule is tight maybe it makes more sense to work on a task that you are comfortable with, so i might be done a bit quicker.